UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-14 files/paper/paper.tex
update

\usepackage{graphicx}
\graphicspath{ {images/}{images/figure1/}{images/figure2/}{images/figure3/} }
%\graphicspath{{images/failures/}}
%\graphicspath{{images/figure1/}}

@@

\section{Experiments}
\subsection{Datasets}
We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
evaluate a tracking algorithm on a diving video taken from Youtube. Subsets of Imagenet containing underwater images
were selected for the training of CycleGAN, and manually separated into two classes. We let $X$ be the set of
underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that
images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
all images in $X$ with $F$. Figure 2 shows sample training pairs.

\subsection{Evaluation}
We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated entirely on the images from the
test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.

@@

@@

@@

\begin{tabular}{l|c|c|c|r}
 \cline{2-5}
 &  Correct detection & Wrong detection & Missed detection & Total \# of frames\\ \hline  \cline{2-4}
On real images  &  42 & 14 & 444 & 500  \\ \hline
On generated images  &  147 & 24 & 329 & 500  \\ \hline
\end{tabular}

@@

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.5cm}}
   % TODO 
   % I couldn't figure out how to get the text centered above the images
   % Also, the numbers below the images should be centered too, and more
   % obviously below the row instead of seemlingly above the next one. Those
   % numbers are the distances in pixel space (normalized between [0,1]) from
   % the edge image to the original edge image.

   5 \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\

%   \includegraphics[width=0.8in]{n01496331_15872_original} &
%   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
%   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
%   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
%   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
%   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
%   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
%   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
   0 & \small{125.78} & \small{80.68} & \small{78.49} \\

%   \includegraphics[width=0.8in]{n01496331_22079_original} &
%   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
%   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
%   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
%   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
%   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
%   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
%   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
   0 & \small{94.57} & \small{38.22} & \small{37.29} \\

%   \includegraphics[width=0.8in]{n02607072_4739_original} &
%   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
%   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
%   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
%   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
%   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
%   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
%   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
   0 & \small{100.69} & \small{87.81} & \small{87.95} \\

>>>>

\usepackage{graphicx}
\graphicspath{ {images/}{images/figure1/}{images/figure2/}{images/figure3/} {images/edges/}}
%\graphicspath{{images/failures/}}
%\graphicspath{{images/figure1/}}

@@

\section{Experiments}
\subsection{Datasets}
We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
evaluate a tracking algorithm on a diving video taken from Youtube
\footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet containing underwater images
were selected for the training of CycleGAN, and manually separated into two classes. We let $X$ be the set of
underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that
images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
all images in $X$ with $F$. Figure 2 shows sample training pairs. When comparing with CycleGAN, we used a test set
acquired from Flickr \footnote{How do I cite Flickr}.

\subsection{Evaluation}
We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate entirely on the images from the
test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.

@@

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm}}

   Original & UGAN & UGAN-P \\

   \includegraphics[width=0.8in]{n01917289_4982_real} &
   \includegraphics[width=0.8in]{n01917289_4982_gen_0} &
   \includegraphics[width=0.8in]{n01917289_4982_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_16340_real} &
   \includegraphics[width=0.8in]{n01496331_16340_gen_0} &
   \includegraphics[width=0.8in]{n01496331_16340_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_22183_real} &
   \includegraphics[width=0.8in]{n01496331_22183_gen_0} &
   \includegraphics[width=0.8in]{n01496331_22183_gen_1} \\

   \includegraphics[width=0.8in]{n01664065_29738_real} &
   \includegraphics[width=0.8in]{n01664065_29738_gen_0} &
   \includegraphics[width=0.8in]{n01664065_29738_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_11938_real} &
   \includegraphics[width=0.8in]{n01496331_11938_gen_0} &
   \includegraphics[width=0.8in]{n01496331_11938_gen_1} \\

   \includegraphics[width=0.8in]{n02606052_2969_real} &
   \includegraphics[width=0.8in]{n02606052_2969_gen_0} &
   \includegraphics[width=0.8in]{n02606052_2969_gen_1} \\

\end{tabular}
\caption{Samples. The network can both recover color and also correct color if a small amount is present.}
\end{figure}

@@

   Original & CycleGAN & UGAN & UGAN-P \\

   \includegraphics[width=0.8in]{1_original} &
   \includegraphics[width=0.8in]{1_cimg} &
   \includegraphics[width=0.8in]{1_u0img} &
   \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{1_oedges} &
   \includegraphics[width=0.8in]{1_cedges} &
   \includegraphics[width=0.8in]{1_u0edges} &
   \includegraphics[width=0.8in]{1_u1edges} \\

   \includegraphics[width=0.8in]{2_original} &
   \includegraphics[width=0.8in]{2_cimg} &
   \includegraphics[width=0.8in]{2_u0img} &
   \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{2_oedges} &
   \includegraphics[width=0.8in]{2_cedges} &
   \includegraphics[width=0.8in]{2_u0edges} &
   \includegraphics[width=0.8in]{2_u1edges} \\

   \includegraphics[width=0.8in]{3_original} &
   \includegraphics[width=0.8in]{3_cimg} &
   \includegraphics[width=0.8in]{3_u0img} &
   \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{3_oedges} &
   \includegraphics[width=0.8in]{3_cedges} &
   \includegraphics[width=0.8in]{3_u0edges} &
   \includegraphics[width=0.8in]{3_u1edges} \\

   \includegraphics[width=0.8in]{4_original} &
   \includegraphics[width=0.8in]{4_cimg} &
   \includegraphics[width=0.8in]{4_u0img} &
   \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{4_oedges} &
   \includegraphics[width=0.8in]{4_cedges} &
   \includegraphics[width=0.8in]{4_u0edges} &
   \includegraphics[width=0.8in]{4_u1edges} \\

@@

\begin{tabular}{l|c|c|c|r|}
 \cline{2-5}
 &  Correct detection & Wrong detection & Missed detection & Total \# of frames\\ \hline  \cline{2-4}
On real images  &  42 & 14 & 444 & 500  \\ \hline
On generated images  &  147 & 24 & 329 & 500  \\ \hline
\end{tabular}

@@
